Super awesome embeddings

### 2019-02-03 paper/main.tex
Fix "average average" typo

\textit{Context embedding} \(\bm{c}\) is also achieved by taking an average of word embeddings (Equation \ref{eq:keyword_embedding}).
In this case, \(N = 2l + 1\) and \(w_1, w_2, ..., w_N\) is the context with ambiguous word inside. For some cases \(N < 2l + 1\), since the ambiguous word may occur at the beginning or ending of text example and full context cannot be collected.
In this case, we just average average the reduced context.

@@

>>>>

\textit{Context embedding} \(\bm{c}\) is also achieved by taking an average of word embeddings (Equation \ref{eq:keyword_embedding}).
In this case, \(N = 2l + 1\) and \(w_1, w_2, ..., w_N\) is the context with ambiguous word inside. For some cases \(N < 2l + 1\), since the ambiguous word may occur at the beginning or ending of text example and full context cannot be collected.
In this case, we just average the reduced context.

@@

\section{Experiments}
\subsection{Assumptions}
Since our goal is to check how embedding approach works for WSD problem, we use pretrained embedding model from spaCy - en\_vectors\_web\_lg.
Due to high impact of training data order on test results, as a result we take average score of 30 runs for each optimization.
\subsection{Baseline}
First of experiments is to check how out-of-the-box model works without extra optimizations. We perform tests with different context lengths, as a score we choose top 1 and top 3 accuracy. Results are shown in the Fig. \ref{fig:baseline}.

\begin{figure}
    \label{fig:baseline}
    \caption{Top accuracy of base model with different context length}
    \includegraphics[scale=0.5]{res/baseline_context_top_acc.png}
\end{figure}
TODO: Some discussion.
\subsection{Context length optimization}
Once we have base model results we check how simple alpha optimization improves accuracy based on context length. To do this, we choose arbitrarily a value for alpha parameter and run tests after one epoch of training the model. Since we average results from 30 runs we mark the measurement uncertainty on the graph. Results are shown in the Fig. \ref{fig:exp1}.
\begin{figure}
    \label{fig:exp1}
    \caption{Comparison of the base model and a little bit optimized model based on different context length}
    \includegraphics[scale=0.6]{res/exp1_context_top_acc.png}
\end{figure}
TODO: Some discussion.

\subsection{Alpha parameter optimization}
Next step is to check the influence of alpha parameter on the accuracy score after one epoch of training with fixed context length - the best value for the base model. Results are shown in the Fig. \ref{fig:exp2}. In this experiment we also mark the measurement uncertainty on the graph.

\begin{figure}
    \label{fig:exp2}
    \caption{Based on fixed context length, comparison of the base model and a model optimized with various alpha parameters. }
    \includegraphics[scale=0.6]{res/exp2_alpha_top_acc.png}
\end{figure}
TODO: Some discussion.
\subsection{Beta parameter optimization}
Next optimization we test is the influence of beta parameter. In this test we also performs one epoch of training with fixed context length and alpha parameter, based on previous experiment's results. Results are shown in the Fig. \ref{fig:exp3}. Since in this case we compare our solution to non-fully deterministic solution we decide to mark only averaged score of performed tests.

\begin{figure}
    \label{fig:exp3}
    \caption{Based on fixed context length and alpha parameter value, comparison of the alpha-optimized model and a alpha-optimized model with various beta parameters. }
    \includegraphics[scale=0.5]{res/exp3_beta_top_acc.png}
\end{figure}
TODO: Some discussion.

\subsection{Longer training}
Previous optimization are applied for only one epoch of training. The goal of next experiment is to check how number of epochs affects final accuracy. We run up to 5 epochs of training using parameters obtained in previous experiments. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_1}
    \caption{5 epoch training of optimized model}
    \includegraphics[scale=0.6]{res/exp4_epoch_top_acc.png}
\end{figure}
We see that there is almost no improvement after first epoch of training. Probably the problem is that alpha and beta parameters are too big. We also check what happens when we choose lower values of alpha/beta parameters. Results are shown in the Fig. \ref{fig:exp4_2}.
\begin{figure}
    \label{fig:exp4_2}
    \caption{Comparison of multiple optimized models across 5 epochs of training. }
    \includegraphics[scale=0.6]{res/exp4_epoch_multiconfiguration_top_acc.png}
\end{figure}
TODO: Some discussion.
